---
title: Predicting the percentage of an studdent based on the no.of study hours using
  linear regression model
author: "Naveen.A"
date: "03/02/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
#Reading the packages required for analysis
library(readr)
library(dplyr)

#Importing the Dataset and storing it into a variable.
student_data <- read_csv("student_scores.csv")
head(student_data) #showing the top 5 data from the table.
```
```{r}
#loading the ggplot2 libraries for plotting the graph
library(ggplot2)

#plotting the graph where the independent variable on the x #axis(hours) and dependent variable on the y axis(scores).
ggplot(data = student_data,
       aes( x = Hours, y = Scores)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```
```{r}
#finding the coefficients of the data using linear model function 

student_lm_fit <- lm(Scores ~ Hours, data = student_data)

summary(student_lm_fit)
```
```{r}
 coef(student_lm_fit) #calling the coefficient value from the summary. that is the intercept and slope.

#finding the expected values i.e predicted value using the observed value.
student_data <- student_data %>% 
  mutate(perc_predictions = fitted(student_lm_fit))
head(student_data)


```
```{r}
#predicted score if a student studies for 9.25 hours
student_score <- coef(student_lm_fit)[[1]] + coef(student_lm_fit)[[2]] * 9.25
student_score
```
```{r}
#The status of students depending upon their scores using case_when function
student_data <- student_data %>% mutate(status = case_when(perc_predictions < 35 ~ "Fail",                  perc_predictions >= 35 & perc_predictions <= 60 ~ "Pass", perc_predictions > 60 & perc_predictions < 85 ~             "first_class",                                            perc_predictions >= 85 ~ "Distinction"))
student_data
```
```{r}
confint(student_lm_fit)


#We can see that there is 97.5% probability that the true unknown value of the coefficient will fall within the specified range.and the intercept falls between the range ( -2.75 to 7.720 ) that is the score if a student studies #for 0 hours. and the hours falls between the range (8.83 - 10.71) that mean there will increase in score between 8.83 - 10.71 if the average of hour increases by 1 hour.
```

##conclusion: We can see that there is 97.5% probability that the true unknown value of the coefficient will fall within the specified range.variables are linear and hence i used linear regression model to predict the dependent/ response variable and we were successful in predicting the score of student studying for 9.25 hours.

